Learning Features and Abstract Actions for Computing Generalized Plans

### 2018-11-06 doc/camera-ready/paper.tex
Correct missing bib ref

An \emph{abstract action}  for a generalized problem $\Q$ and a set $F$ of features
is a pair $\bar{a}=\abst{Pre}{\Eff}$ where $Pre$ and $\Eff$ are the  preconditions
and effects expressed in terms of the  set $V_F$ of boolean and numerical \emph{state variables}
associated with the features. Preconditions and effects over boolean state variables $p$ are literals of the form $p$
and $\neg p$, that abbreviate the  atoms $p=true$ and $p=false$, while
preconditions over  numerical state variables $n$ are of  the form $n=0$ and $n > 0$,
and effects of the form  $n\mminus$ (decrements) and  $n\pplus$ (increments).
The language for the abstraction,  that combines boolean with numerical variables
that can be decreased or increased by unspecified amounts, is the language of the \emph{qualitative numerical problems (QNPs)},
that unlike standard numerical planning problems \cite{helmert:numerical-undecidable}
are decidable and can be solved effectively by means of  FOND planners \cite{srivastava:aaai2011,bonet:ijcai2017}.

>>>>

An \emph{abstract action}  for a generalized problem $\Q$ and a set $F$ of features
is a pair $\bar{a}=\abst{Pre}{\Eff}$ where $Pre$ and $\Eff$ are the  preconditions
and effects expressed in terms of the  set $V_F$ of boolean and numerical \emph{state variables}
associated with the features. Preconditions and effects over boolean state variables $p$ are literals of the form $p$
and $\neg p$, that abbreviate the  atoms $p=true$ and $p=false$, while
preconditions over  numerical state variables $n$ are of  the form $n=0$ and $n > 0$,
and effects of the form  $n\mminus$ (decrements) and  $n\pplus$ (increments).
The language for the abstraction,  that combines boolean with numerical variables
that can be decreased or increased by unspecified amounts, is the language of the \emph{qualitative numerical problems (QNPs)},
that unlike standard numerical planning problems \cite{helmert:numerical}
are decidable and can be solved effectively by means of  FOND planners \cite{srivastava:aaai2011,bonet:ijcai2017}.
